Radioastronomical image reconstruction using Kalman filter under ionospheric perturbations

### 2022-08-15 article/article.tex
dir4 graphs

	The first interesting observations on these graphs are the extremities convergences : above 0,05m position error standard deviation, errors approach a distance of 0,1. The $d_1$ distance being normalised (as $\x$ and $\xe$ are normalised between 0 and 1), this distance means 10\% reconstruction error. This error level represents non reliable reconstruction. It can be illustrated by the following reconstruction :
	\begin{figure}[H]
		\centering
		\begin{subfigure}{.5\textwidth}
			\centering
			\includegraphics[width=.7\linewidth]{src/t_im.png}
			\caption{True image}
		\end{subfigure}%
		\begin{subfigure}{.5\textwidth}
			\centering
			\includegraphics[width=.7\linewidth]{src/t_err.png}
			\caption{Reconstruction at 0,1 distance of the true image}
		\end{subfigure}
		\caption{Image reconstruction at unreliable distance}
	\end{figure}

	This distance around 0,1 is actually expected, as the mean distance $d_1$ between two random matrices in $\mathcal{M}_{10}([0;1])$ can be computed and gives 1,167. The random effects of position errors getting more important, the reconstruction using this inaccurate positions matrix is becoming random thus converging to this value of 1,167.

@@

@@

>>>>

	The first interesting observations on these graphs are the extremities convergences : above 0,05m position error standard deviation, errors approach a distance of 0,1. The $d_1$ distance being normalised (as $\x$ and $\xe$ are normalised between 0 and 1), this distance means 10\% reconstruction error. This error level represents non reliable reconstruction. It can be illustrated by the following reconstruction :
	\begin{figure}[H]
		\centering
		\begin{subfigure}{.5\textwidth}
			\centering
			\includegraphics[width=.7\linewidth]{src/t_im.png}
			\caption{Errorless reconstruction}
		\end{subfigure}%
		\begin{subfigure}{.5\textwidth}
			\centering
			\includegraphics[width=.7\linewidth]{src/t_err.png}
			\caption{Reconstruction at 0,1 distance of the true image}
		\end{subfigure}
		\caption{Image reconstruction at unreliable distance}
	\end{figure}

	This distance around 0,1 is actually expected, as the mean distance $d_1$ between two random matrices in $\mathcal{M}_{10}([0;1])$ can be computed and gives 1,167.\footnote{computed as the mean $d_1$ distance between two randomly generated matrices using matlab function \mintinline{matlab}|rand|, repeated $10^4$ times} The random effects of position errors getting more important, the reconstruction using this inaccurate positions matrix is becoming random thus converging to this value of 1,167. \\

	On the other side of the graph, the distance seems to converge to a value around $3\times10^{-4}$. This value is rather unexpected, as it is below the errorless reconstruction error. This may be explained by the complex nature of the reconstructed image, but no certain explanation was found. The convergence part is also uncertain, as the mean values seems to converge but the standard deviation expands. The convergence at non-zero distance of the errorless reconstruction is also unexplained.

@@

	Ionospheric perturbations being local and direction-dependent, it can be interesting to measure the effect of a single direction being inaccurate. To evaluate the reconstruction error, the $d_2$ distance is used, as it is additive: the total distance between two reconstructions is the sum of the distance of each direction.

@@

	\newpage
	\part{Conclusion}
